Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-03 Latex/journal_v1/V5/pr.tex
finish analyse journal

\begin{figure*}
  \centering 
    \includegraphics[scale = 0.75]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.

@@

T^{tot} &=  T^{process} + T^{transmission} + T^{propagation}\\
T^{process} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
T^{transmission} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
T^{propagation} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\

@@

The total delay ($T^{tot}$) is the sum of the processing delay ($T^{process}$), the transmission delay ($T^{transmission}$), and the propagation delay($T_{propagation}$). 
The propagation delay is the time takes for a signal to reach its destination. So it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal).

@@

Here we assume the value of propagation delay and transmission is negligible compared to the rest.

@@

T^{tot} \approx T^{process}

@@

Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follows, respectively.

@@

T^{process}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}

@@

Hence, $T^{tot}_{u(s,i)} \approx T^{process}_{u(s,i)} $

@@

\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r

@@

&\bar{\mathcal{R}}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\

@@

& C^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 
&T_{tot}^{u(s,i)}  \leq T_{max}^{s} \quad \forall i,\forall s,\label{c16} \\

@@

& 0 \leq M_s \leq M^{max}  \quad \forall s,\label{c16-3}\\

@@

& \phi_{tot}  \leq \phi_{max}, \label{c19} \\

@@

where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
\eqref{c11}, and \eqref{c12}, indicate that the power of each O-RU does not exceed the maximum power, and the power of each UE is a positive integer value, respectively.  

@@

In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We simplified and reformulated MINL parts and used an iterative heuristic algorithm to solve the problem.
We solve this problem in two-level iteratively until it converges. In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters to turn them into a jointly-convex problem; Afterward, we solve it by dual optimization problem.
In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and number of VNFs.   
We repeat this procedure until the algorithm converges.

@@

As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$, the lower bound $\bar{\rho}_{u(s,i)}^{k}$ 
for $\rho_{u(s,i)}^{k}$ 
and the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.

@@

Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,

@@

So the given assumption leads to have same energy for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 

@@

T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.

@@

In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below

@@

&T_{max}^s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\

@@

Thus, if we restrict \eqref{c16} to equality we have

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

In \eqref{eqDelay}, $0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have same sign. Using \eqref{c16-2},
in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and to simplify the problem, assume 
$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \geq 1$ since the order of $T_{max}^s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T_{max}^s$.
Therefore, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T_{max}^s$.
So the numerator is positive.
In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T_{max}^s$ as mentioned above.
Therefore, we need to have constraints below
\begin{equation}\label{constraint16}
\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
The left side of this formula leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
\begin{equation}\label{RM}
\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s},\\
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$.
So we have,
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{lemma}
Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
So the simplest approach is to relax $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
By taking derivatives of \eqref{lagrang} (the lagrangian function), with respect to the $\boldsymbol{P}$ and the $\boldsymbol{E}$, these two variables are obtained.
Assume, $e_{r,u(s,i)}^{k} = 1$
\begin{equation}\label{deriveP}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
Where
\mathfrak{D}_{r,u(s,i)}^{k} &= |\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
where $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
p_{r,u(s,i)}^{k} = [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment is obtained as follow
\begin{equation}\label{deriveE}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\

>>>>

\begin{figure*}
  \centering 
    \includegraphics[scale = 0.7]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.

@@

T^{tot} &=  T^{proc} + T^{tr} + T^{pro}\\
T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t}  \\
T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}  \\

@@

The total delay ($T^{tot}$) is the sum of the processing delay ($T^{proc}$), the transmission delay ($T^{tr}$), and the propagation delay($T^{pro}$). 
The propagation delay is the time takes for a signal to reach its destination. So it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal). So the total propagation delay ($T^{pro}$) is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{mid,p}$, and the backhaul $T^{b,p}$.

@@

So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{mid,t}$, and the backhaul $T^{b,t}$.
Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.

@@

T^{tot} \approx T^{proc}

@@

Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively.

@@

T^{proc}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}

@@

Hence, $T^{tot}_{u(s,i)} \approx T^{proc}_{u(s,i)} $

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\

@@

& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
&T^{tot}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\

@@

& \phi^{tot}  \leq \phi^{max}, \label{c19} \\

@@

where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.
\eqref{c11}, \eqref{c12} and \eqref{c12-1}, indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.  

@@

In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this problem is non-convex and it is a  mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We applied some simplifications and used an iterative heuristic algorithm to solve the problem.
We solve this problem in two-level iteratively until it converges \cite{ali2018joint}.

In the first level, the principal purpose is to allocate adequate PRBs and the power to the UEs and allocate enough activated VNFs
to each slice. So, at this level, we want to obtain the variables $\boldsymbol{P}, \boldsymbol{E},$ and $\boldsymbol{M}$.
Despite the simplification of the problem
\eqref{problem}, it is still NP-hard and challenging to solve. Therefore,
we relax the variable $\boldsymbol{E}$ \cite{lee2018dynamic,ali2018joint} and reformulating the constraint \eqref{c16},
to turn them into a jointly-convex problem; Afterward, we solve this problem using a conventional dual Lagrangian method. 
In the second level, finding the optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation, and the number of activated VNFs.   
We repeat this procedure until the algorithm converges.

@@

As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in the \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$. 
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in the \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in the \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.

@@

Consider UPF, O-CU and O-DU use the processors with the same processing capability. (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,

@@

Moreover, the given assumption leads to have same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result of these assumption, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ 

@@

T^{proc}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
T^{proc}_{s} &=  T^{RU}_{s} + 3\times T^{DU}_{s}.

@@

In the problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below

@@

&T^{max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\

@@

Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
Also, we have the following inequality.

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have the same sign.
In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
So the numerator will be positive.
In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
$\mu_s \geq 0$ and
$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
%Therefore, we need to have the constraint below.
%\begin{equation}\label{constraint16}
%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
%\end{equation}

The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
\begin{equation}\label{RM}
\begin{split}
\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
 \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\end{split}
\end{equation}
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as follow.
\begin{equation}
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{equation}
\end{lemma}
Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
So the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
\begin{equation} \label{pr11}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{min}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$, $\boldsymbol{\mathfrak{q}}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\begin{alignat}{4}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
\end{alignat}
\end{subequations}
\begin{lemma}

The derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{P}$ and $\boldsymbol{E}$ give the Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal value of these two variables \cite{lee2018dynamic,ali2018joint}.
